---
title: "Daily Aggregated Beans Stock Report"
author: "SAKiRP"
date: "`r Sys.Date()`"
format: html

---

## Aggregation Summary

Below are the amount of bean stock currently aggregated in AMCOS in Kigoma.

```{r, include=FALSE}
#| label: load-pkgs
#| code-summary: "Packages"
#| message: false

library(tidyverse)  
library(chronicle)      
library(RPostgres)
library(httr)

con = DBI::dbConnect(odbc::odbc(), "PostgreSAKiRP")
waeo = dbReadTable(con,"waeos")
district = dbReadTable(con, "districts")
ward = dbReadTable(con,"wards")
village = dbReadTable(con,"villages")
faab = dbReadTable(con,"faab_coach")
amcos = dbReadTable(con,"amcos")

stock_url = "https://kc.humanitarianresponse.info/api/v1/data/1026275.csv"
stock_rawdata = GET(stock_url,authenticate(Sys.getenv("sakirp_user"),Sys.getenv("sakirp_pw")))
stock_content = content(stock_rawdata,"raw",encoding="UTF-8")
stock_data_raw = read_csv(stock_content) %>% 
  janitor::clean_names()

stock_data_clean = stock_data_raw %>% 
  mutate(
    survey_info_waeo = na_if(survey_info_waeo,"n/a"),
    survey_info_waeo = as.numeric(survey_info_waeo),
    survey_info_faab = na_if(survey_info_faab,"n/a"),
    survey_info_faab = as.numeric(survey_info_faab)
  ) %>% 
  rename(
    njano_in = ends_with("njano_in"),
    stock_beans = ends_with("closing_stock_bt"),
    stock_calima = survey_info_summary_beans_closing_stock_calimat,
    stock_red = survey_info_summary_beans_closing_stock_redt,
    stock_uyole = survey_info_summary_beans_closing_stock_njano_uyolet,
    stock_njano = survey_info_summary_beans_closing_stock_njanot
  ) %>% 
  left_join(district, by=c("survey_info_district"="id")) %>% 
  left_join(ward, by=c("survey_info_ward"="id")) %>% 
  left_join(waeo, by=c("survey_info_waeo"="id")) %>% 
  left_join(faab, by=c("survey_info_faab"="id")) %>% 
  left_join(amcos, by=c("survey_info_amcos"="id")) %>%
  mutate(
    data_collector = case_when(
      !is.na(waeo) ~ waeo,
      !is.na(name) ~ name
    )
  )

faab_data = stock_data_clean %>% 
  filter(!is.na(survey_info_faab))

waeo_data = stock_data_clean %>% 
  filter(!is.na(survey_info_waeo))

warehouse_stock = function(data) {
  data %>% 
    select(endtime,district=district.x,ward=ward.x,data_collector,
           amcos,stock_beans) %>% 
    group_by(district,ward,amcos) %>% 
    filter(endtime == max(endtime)) %>% arrange(amcos)
}

warehouse_variety_stock = function(data) {
  data %>% 
    select(endtime,District=district.x,
           Ward = ward.x,amcos,data_collector,stock_calima,stock_red,stock_njano,
           stock_uyole,stock_beans) %>% 
    group_by(District,Ward,amcos) %>% 
    filter(endtime == max(endtime)) %>% 
    arrange(amcos)
}


faab_data_summary = warehouse_stock(faab_data) %>%
  ungroup() %>% 
  mutate(
    `Data Entry` = lubridate::ymd(as.Date(endtime)),.before=district,
    `Target (MT)` = case_when(
      amcos=="Muhange" ~ 250,
      amcos=="Nkuchikeka" ~ 150,
      amcos=="Kurugongo" ~ 144,
      amcos=="Kanyonza" ~ 320,
      amcos=="Kitahana" ~ 88,
      amcos=="Motomoto" ~ 152,
      amcos=="Ruti" ~ 210,
      amcos=="Twikome" ~ 202,
      amcos=="Ubhumwe" ~ 123,
      amcos=="Kiziguzigu" ~ 410,
      amcos=="Kibondo-Mjini" ~ 140,
      amcos=="Kibondo-Bunyambo" ~ 140,
      amcos=="Nyakitonto" ~ 330,
      amcos=="Kaziju" ~ 90,
      amcos=="Nyamuki" ~ 15
    ),
    `Actual (MT)` = round((stock_beans/1000),1),
    Progress = round((`Actual (MT)`/`Target (MT)`)*100,0)
  ) %>% 
  select(`Data Entry`,District=district,Ward=ward,AMCOS=amcos,`Target (MT)`,`Actual (MT)`,Progress) %>% 
  arrange(-`Actual (MT)`)

total_beans = sum(faab_data_summary$`Actual (MT)`)

variety_data_summary = warehouse_variety_stock(faab_data) %>% 
  ungroup() %>% 
  mutate(
    `Data Entry` = lubridate::ymd(as.Date(endtime)),.before=District,
    `Rose Coco (MT)` = round((as.numeric(stock_calima)/1000),1),
    `Red Kidney (MT)` = round((as.numeric(stock_red)/1000),1),
    `Kigoma Njano (MT)` = round((as.numeric(stock_njano)/1000),1),
    `Uyole Njano (MT)` = round((as.numeric(stock_uyole)/1000),1),
    `Actual (MT)` = round((stock_beans/1000),1),
  ) %>% 
  select(
    `Data Entry`,District,Ward,AMCOS=amcos,
    `Rose Coco (MT)`:`Actual (MT)`
  ) %>% arrange(-`Actual (MT)`)

```

There is a total of **`r total_beans` tonnes** of aggregated beans as of **`r Sys.Date()`** .

@fig-histogram is a graphical summary of available bean stock at AMCOS warehouses.

```{r}
#| echo: false
#| label: fig-histogram
#| fig-cap: "Aggregated beans stock"
#| fig-height: 6
#| fig-width: 10

plot = ggplot(faab_data_summary, aes(reorder(AMCOS,`Actual (MT)`),`Actual (MT)`)) +
  geom_col() + 
  coord_flip() +
  theme_bw() +
  xlab(NULL) + 
  ylab(NULL) +
  #labs(title = "Aggregated stocks at AMCOS warehouses") +
  theme(text = element_text(size = 20)) +
  geom_text(aes(label = `Actual (MT)`), hjust = 1.2,colour="white")

plot
```

The tabular summary is as in @tbl-summary:

```{r}
#| echo: false
#| label: tbl-summary
#| tbl-cap: "Aggregated beans (Metric Tonnes)"

faab_data_summary %>% 
  mutate(
    `Actual (MT)` = kableExtra::cell_spec(
      `Actual (MT)`, background = ifelse(Progress > 70,"green",
                                    ifelse(Progress < 30,"red","orange"))),
    `Last Update (Hours)` = as.double(difftime(lubridate::ymd(`Data Entry`),
                   lubridate::ymd(lubridate::today()),
                   units = "hours")),
    `Data Entry` = kableExtra::cell_spec(
      `Data Entry`, background = ifelse(`Last Update (Hours)` < -24,"red",
                                    "green"))
  ) %>% 
  select(-Progress) %>% 
  kableExtra::kable(escape = FALSE,format = "html", booktabs = T) %>% 
  kableExtra::kable_styling(latex_options="scale_down")

```
::: callout-warning
Data Entry color codes are: red = \> 24 hours stale, green = \< 24 hours stale

:::

::: callout-note
Progress color codes are: red = 0-30%, orange = 30-70% and green = \>70%.

Black = Not Available
:::

@tbl-variety summarises bean varieties available as of **`r Sys.Date()`** .

```{r variety_data_summary}
#| echo: false
#| label: tbl-variety
#| tbl-cap: "Available bean varieties"
variety_data_summary %>% 
  mutate(
    `Rose Coco (MT)` = kableExtra::cell_spec(
      `Rose Coco (MT)`, background = ifelse(`Rose Coco (MT)` %in% c(0,NA),"black",
                                    "white")),
    `Red Kidney (MT)` = kableExtra::cell_spec(
      `Red Kidney (MT)`, background = ifelse(`Red Kidney (MT)` %in% c(0,NA),"black",
                                    "white")),
    `Kigoma Njano (MT)` = kableExtra::cell_spec(
      `Kigoma Njano (MT)`, background = ifelse(`Kigoma Njano (MT)` %in% c(0,NA),"black",
                                    "white")),
     `Uyole Njano (MT)` = kableExtra::cell_spec(
      `Uyole Njano (MT)`, background = ifelse(`Uyole Njano (MT)` %in% c(0,NA),"black",
                                    "white"))
  ) %>% 
  kableExtra::kable(escape = FALSE,format = "html", booktabs = T) %>% 
  kableExtra::kable_styling(latex_options="scale_down")


```

<!--# ADD SECTION HEADING FOR REFERENCES HERE -->
